Eye-tracking

### 2019-02-15 ngrams/prelim_ngrams.Rmd
cleaned up ngrams rmd

```{r corpora}
prov_utterances <- get_utterances(corpus = "Providence") %>% 
  filter(speaker_role != "Target_Child") %>%
  mutate(words = stem)

okayama_utterances <- get_utterances(corpus = "Okayama")  %>% 
  filter(speaker_role == "Target_Child") %>%
  rename(words = gloss)

@@

@@

```{r ngram entropy}
# unnest_tokens(word, value, token = stringr::str_split, pattern = " +")

# takes in a tbl of utterances the column with the actual utterances is 
# named words, along with an integer target_length and a ngram length N.
ngram_entropy <- function(utterances, target_length, N) {

@@

```{r childes}
## Providence
# unigrams
prov_unigrams <- map(2:10, ~ngram_entropy(prov_utterances, .x, 1)) %>% 
  bind_rows()

@@

## Zhou
# unigrams
zhou_unigrams <- map(2:10, ~ngram_entropy(zhou_utterances, .x, 1)) %>% 
  bind_rows()

zhou_unigrams %>% ggplot(aes(x = gram_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  geom_pointrange() +
  geom_smooth(se = F)

# bigrams
zhou_bigrams <- map(3:10, ~ngram_entropy(zhou_utterances, .x, 2)) %>% 
  bind_rows()

zhou_bigrams %>% ggplot(aes(x = gram_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  geom_pointrange() +
  geom_smooth(se = F)

# trigrams
zhou_trigrams <- map(4:10, ~ngram_entropy(zhou_utterances, .x, 3)) %>% 
  bind_rows()

zhou_trigrams %>% ggplot(aes(x = gram_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  geom_pointrange() +
  geom_smooth(se = F)

## Okayama
# bigrams 
okayama_bigrams <- map(3:10, ~ngram_entropy(okayama_utterances, .x, 2)) %>% 
  bind_rows()

okayama_bigrams %>% ggplot(aes(x = gram_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  geom_pointrange() +
  geom_smooth(se = F)

# trigrams
okayama_trigrams <- map(4:10, ~ngram_entropy(okayama_utterances, .x, 3)) %>% 
  bind_rows()

okayama_trigrams %>% ggplot(aes(x = gram_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  geom_pointrange() +
  geom_smooth(se = F)
```

```{r zhou and okayama}
# bigrams
prov_bigrams <- map(3:10, ~ngram_entropy(prov_utterances, .x, 2)) %>% 
  bind_rows()

```

>>>>

```{r corpora}
prov_utterances <- get_utterances(corpus = "Providence") %>% 
  filter(speaker_role == "Target_Child") %>%
  mutate(words = stem)

okayama_utterances <- get_utterances(corpus = "Okayama")  %>% 
  filter(speaker_role != "Target_Child") %>%
  rename(words = gloss)

@@

shiro_utterances <- get_utterances(corpus = "Shiro") %>% 
  filter(speaker_role == "Target_Child") %>%
  rename(words = gloss)

wagner_utterances <- get_utterances(corpus = "Wagner") %>% 
  filter(speaker_role == "Target_Child") %>%
  rename(words = gloss)

@@

```{r ngram entropy}
# takes in a tbl of utterances the column with the actual utterances is 
# named words, along with an integer target_length and a ngram length N.
ngram_entropy <- function(utterances, target_length, N) {

@@

```{r childes}
## Providence
# unigrams to check against previous results
prov_unigrams <- map(2:10, ~ngram_entropy(prov_utterances, .x, 1)) %>% 
  bind_rows()

@@

write_feather(prov_unigrams, "prov/child_unigrams.feather")
```
